Cerebral oxygenation manuscript figures

### 2022-02-09 final_figures.Rmd
add NIRS median, q1, q3 to manuscript tables file

@@

>>>>

```{r fig_1_and_2_stats, eval = FALSE}

df_fig1_fig2_stats <-

  df_fig1 %>% 
    group_by(variable, status) %>% 
    dplyr::select(value) %>% 
    summarise_all(funs(median = median, q1 = quantile(., probs = 0.25), q3 = quantile(., probs = 0.75)), na.rm = TRUE) %>% 
    mutate_if(is.numeric, round, 2) %>%

  bind_rows(

    df_fig2 %>% 
      group_by(variable, status) %>% 
      dplyr::select(value) %>% 
      summarise_all(funs(median = median, q1 = quantile(., probs = 0.25), q3 = quantile(., probs = 0.75)), na.rm = TRUE) %>% 
      mutate_if(is.numeric, round, 2)

@@

sheet = createSheet(wb, "Figs 1 & 2 stats")

  addDataFrame(df_fig1_fig2_stats %>% as.data.frame(), sheet = sheet, startColumn = 1, row.names = FALSE)
